Reassessing the Impact of Dynamic Slicing in SFL

### 2018-11-16 paper/main.tex
pass on intro

\Sof{Elaborate more on the advantages of the SFL+DS combination and how DS helps SFL being more efficient}

%% PROBLEM MOTIVATION
Software debugging is difficult. The task of locating the faulty code
(\ie{}, fault localization) is particularly challenging. For that
reason, countless automated techniques have been proposed in the past
to reduce the cost of fault localization. Among those are Dynamic Slicing
(\ds{}) and Spectrum-Based Fault Localization (\sfl{}). Dynamic
Slicing~\cite{Agrawal:1990:DPS:93542.93576} takes as input a failing
test and produces on output a set of statements that influence the
evaluation of the fault-revealing assertion. Although the technique
has been intensively explored, few slicing applications became
popular---WhyLine~\cite{Ko:2008:DRA:1368088.1368130} being an
exception.  \sfl{}~\cite{7390282} is another popular automated
debugging technique. It is a statistical fault localization method
that computes suspiciousness values associated with program entities
(e.g., basic blocks) using coverage information of passing and failing
test cases. \sfl{} produces a list of program entities ranked in
decreasing order of suspiciousness. Likewise dynamic slicing, \sfl{}
received tremendous attention over the years, but its applicability to
support debugging remains
questionable~\cite{ang-perez-van-deursen-rui-2017,Pearson:2017:EIF:3097368.3097441,Xie:2016:RAD:2884781.2884834}.
Despite the skepticism of the research community, \sfl{} has been
shown useful in supporting downstream analyses, such as Automated
Program Repair
(\apr{})~\cite{automatic-software-repair-survey2017,kim-etal-daghstul2017},
an increasingly popular technique that looks for likely fixes to
likely buggy statements. Tools like JAFF \cite{arcuri-2011}, Prophet
\cite{long-rinard-2016}, SemFix \cite{nguyen-qi-roychoudhury-2013},
and SPR \cite{long-rinard-2015} use \sfl{} to guide the search for
likely fixes. \Sof{likely appears too many times on the last 3 lines.}

@@

\ds{} and \sfl{} are complementary. Conceptually, \ds{} identifies
irrelevant parts of the code whereas \sfl{} ranks the relevant parts of
the code.  This paper reports the results of an empirical study to
evaluate the impact of \ds{} to improve \sfl{}. The intuition for the
\comb{} combination is that several highly ranked statements, albeit
covered by failing executions, may be unrelated to the fault. Prior
work reported promising results in this combination
\cite{Wotawa:2010:FLB:1848650.1849235,Alves:2011:FUD:2190078.2190115,DBLP:conf/ecai/HoferW12,lei-mao-dai-wang-2012}.
For example, Lei \etal{}~\cite{lei-mao-dai-wang-2012} reported a
reduction of 78.3\% in \emph{effort}~\cite{7927959} to analyze
rankings when using dynamic slicing in combination with \sfl{} versus
plain \sfl{}. We found surprising that, despite these findings,
reported nearly 5 years ago, no tool or client analyses use this
combination today. One hypothesis to explain that observation is that
results reported in prior work are not as good as it seems. Prior
research evaluated \sfl{} using relative metrics, based on the
position of the first faulty statements found in the ranking relative
to the total number of ranking statements, which is often a very high
number. Ang \etal~\cite{ang-perez-van-deursen-rui-2017} recently
pointed to that fact encouraging developers to adopt precise metrics
such as top-k
\cite{Wu:2014:CLC:2610384.2610386,Lucia:2014:FFL:2642937.2642983,Wen:2016:LLB:2970276.2970359}. \Sof{Elaborate k}The goal of this paper is to reassess whether the \comb{} combination is
worthwhile under the light of this metric and using a larger
dataset. The test suite used for the empirical evaluation is the defect4j dataset which is about twice larger than the biggest test suite used in previous studies. Developers of \acrAbrev{} techniques may directly benefit
from these results~---~either to improve their results or to be aware
they should not invest on this integration. 
%% ~\cite{Jin:2013:FFL:2483760.2483763,Laghari:2016:FSB:2970276.2970308,campos-etal-ase2016,DBLP:journals/stvr/LiuLNBB16,DBLP:conf/hvc/LidO16,7589823}

This research aims to address the doubts surrounding the efficiency of \sfl{}+\ds{} combination through the answer to the following research questions (\RQ{}):

\begin{itemize}[leftmargin=*]
	\item[] \textbf{\RQ{}1} \textit{Does the critical slice include the faulty statements?}
	\item[] \textbf{\RQ{}2} \textit{How many test cases have the faulty statements in the top-5 of classes with the highest suspiciousness ranks?}
	\item[] \textbf{\RQ{}3} \textit{How effective is the \sfl{}+\ds{} combination for bug localization?} 
\end{itemize}

A couple of different tools were designed to perform this empirical study: \morpho{} and \lithium{}. \morpho{} retrieves as an output the input for \lithium{}. \lithium{} uses the input to reduce the search domain for \sfl{} and outputs the statements that resulted from the minimization. \morpho{} uses this to update the spectrum matrix, performs the before and after \sfl{} evaluation using the corresponding matrix, and outputs the metrics that report the \sfl{} performance for both cases ~---~ before and after using \ds{}.

The most significant contributions of this research for the testing community are the following ones:
\begin{itemize}
	\item The presentation of a more extensive evaluation on the efficiency of combining \sfl{} and \ds{} for bug localization in \emph{Java} faulty programs.
	\item Insights into the use of top-k metric to evaluate the classes with the highest suspiciousness ranks.
	\item Both tools are open-source (\morpho{} and \lithium{}), so other researchers can replicate or extent the current research. Benchmarks and experimental results are also publicly available.
\end{itemize}

\Sof{@TODO: sections organization paragraph}

This paper is organized as follows: ....

@@

Spectrum-based fault localization (\sfl) is a statistical fault
localization technique that takes as input a test suite including at
least one failing test and reports on output a ranked list of
components likely to be in fault~\cite{FLSurvey2016,
  DBLP:conf/kbse/JonesH05, DBLP:journals/smr/LuciaLJTB14,
  DBLP:journals/jss/AbreuZGG09}. The following are given in \sfl{}: a
finite set $\mathcal{C} = \set{c_1,c_2,...,c_M}$ of $M$ system
\emph{components}\footnote{A component can be any source code artifact
  of arbitrary granularity such as a class, a method, a statement, or
  a branch~\cite{DBLP:journals/stvr/HarroldRSWY00}.}; a finite set
$\mathcal{T} = \set{t_1,t_2,...,t_N}$ of $N$ system transactions,
which correspond to records of a system execution, such as test cases;
the error vector $e = \set{e_1,e_2,...,e_N}$, where $e_i = 1$ if
transaction $t_i$ has failed and $e_i = 0$ otherwise; and an $N \times
M$ coverage matrix $\mathcal{A}$, where $\A{ij}$ denotes the coverage
of component $c_j$ in transaction $t_i$.  The pair $(\mathcal{A},e)$
is commonly referred to as
spectrum~\cite{DBLP:journals/stvr/HarroldRSWY00}. Figure~\ref{fig:spectrum-example}
shows an example spectrum.
\begin{wrapfigure}[8]{r}{0.29\textwidth}
  \vspace{-2ex}
  \hspace{-3ex}
  \centering
  \small
  \begin{tabular}{c|cccc|c}
    $\mathcal{T}$ & $c_1$    & $c_2$    & $\cdots$ & $c_M$    & $e$    \\ \hline
    $t_1$         & $\A{11}$ & $\A{12}$ & $\cdots$ & $\A{1M}$ & $e_1$  \\
    $t_2$         & $\A{21}$ & $\A{22}$ & $\cdots$ & $\A{2M}$ & $e_2$  \\
    \vdots        & \vdots   & \vdots   & $\ddots$ & \vdots   & \vdots \\
    $t_N$         & $\A{N1}$ & $\A{N2}$ & $\cdots$ & $\A{NM}$ & $e_N$  \\
  \end{tabular}
  \caption{An example spectrum.}
  \label{fig:spectrum-example}
\end{wrapfigure}
Several types of spectra exist.  The most commonly used is called
hit-spectrum, where the coverage matrix is encoded in terms of binary
\emph{hit} (1) and \emph{not hit} (0) flags, \ie{}, $\A{ij} = 1$ if
$t_i$ covers $c_j$ and $\A{ij} = 0$ otherwise.  The pair
$(\mathcal{A},e)$ serves as input to the fault localization technique.
With this input, the next step in this coverage-based technique
consists of determining what columns of the matrix $A$ resemble the
error vector $e$ the most.  For that, an intermediate component
frequency aggregator $n_{pq}(j)$ is computed $n_{pq}(j) = |\{i\mid
\A{ij}=p \wedge e_i=q\}|$. $n_{pq}(j)$ denotes the number of runs in
which the component $j$ has been active during execution ($p = 1$) or
not ($p=0$), and in which the runs failed ($q = 1$) or passed ($q =
0$).  For instance, $n_{11}(j)$ counts the number of times component
$j$ has been involved ($p = 1$) in failing executions ($q = 1$),
whereas $n_{10}(j)$ counts the number of times component $j$ has been
involved in passing executions. We then calculate similarity to the
error vector by means of applying \emph{fault predictors} to each
component to produce a score quantifying how likely it is to be
faulty.  Components are then ranked according to such likelihood
scores and reported to the user. Ochiai is one of those fault
predictors that has shown to perform well ~\cite{Pearson:2017:EIF:3097368.3097441,7390282}. \Sof{@Rui, please check if the papers are correct} The Ochiai
formula~\cite{DBLP:conf/prdc/AbreuZG06} is given by
\[\N{11}/(\sqrt{\N{11}+\N{01}} + \sqrt{\N{11}+\N{10})}\]

@@

@@

Following other recent studies, we used the \dfj{} benchmark in our
experiments~\cite{just-defects4j-issta2014}. The \dfj{} benchmark
includes six subjects and 395 faults.
\lang{} is a library
that provides a set of helper utilities for the {\small\texttt{java.lang}}
API. \cmath{} is a lightweight library of self-contained
mathematics and statistics components. The \closure{} is a toolset for
turning JavaScript files into smaller scripts for faster
download and execution in the browser. \chart{} is a library with a
full-featured charts user interface for Java. \jtime{} is a
lightweight library that aims to replace the default Java
{\small\texttt{java.util.Date}} classes providing simpler APIs. \mockito{} is
a mocking testing framework.\comments{ that enables the developer to simulate
the behavior of classes that cannot be used in unit testing.}

>>>>

%\Sof{Elaborate more on the advantages of the SFL+DS combination and how DS helps SFL being more efficient}

%% PROBLEM MOTIVATION
Software debugging is difficult. The task of locating the faulty code
(\ie{}, fault localization) is particularly challenging. For that
reason, countless automated techniques have been proposed in the past
to reduce the cost of fault localization.

Dynamic Slicing (\ds{}) and Spectrum-Based Fault Localization (\sfl{})
are two very popular techniques that use different principles to
automate debugging. Dynamic
Slicing~\cite{Agrawal:1990:DPS:93542.93576} looks for the statements
in code that influence the evaluation of the fault-revealing
assertion. Although the technique has been intensively investigated in
research, few use cases gained
notoriety---WhyLine~\cite{Ko:2008:DRA:1368088.1368130} being an
exception.  \sfl{}~\cite{7390282}, in contrast, does not try to
recover the influence region of faulty statements. It is a black-box
statistical fault localization method that computes suspiciousness
values associated with program entities (e.g., basic blocks). For
that, it uses coverage information of passing and failing test
cases. \sfl{} produces a list of program entities ranked in decreasing
order of suspiciousness. Similarly to \ds{}, \sfl{} received
tremendous attention over the years, but its applicability to support
debugging remains
questionable~\cite{ang-perez-van-deursen-rui-2017,Pearson:2017:EIF:3097368.3097441,Xie:2016:RAD:2884781.2884834}.
Despite the skepticism of the research community, \sfl{} has been
shown useful in supporting downstream analyses, such as Automated
Program Repair
(\apr{})~\cite{automatic-software-repair-survey2017,kim-etal-daghstul2017},
an increasingly popular technique that looks for fixes to buggy
statements. Tools like JAFF \cite{arcuri-2011}, Prophet
\cite{long-rinard-2016}, SemFix \cite{nguyen-qi-roychoudhury-2013},
and SPR \cite{long-rinard-2015} use \sfl{} to guide the search for
likely fixes.

@@

%% For example, Lei \etal{}~\cite{lei-mao-dai-wang-2012} reported a
%% reduction of 78.3\% in \emph{effort}~\cite{7927959} to analyze
%% rankings when using dynamic slicing in combination with \sfl{} versus
%% plain \sfl{}.

\ds{} and \sfl{} are complementary. Intuitively, \ds{} identifies
irrelevant parts of the code whereas \sfl{} ranks the relevant parts
of the code.  This paper reports the results of a comprehensive study
to evaluate the impact of \ds{} to improve \sfl{}. The study involves
\numFaults{} faults from \numPrograms{} programs from the Defects4J (D4J)
dataset~\cite{just-defects4j-issta2014}, which is frequently used to
evaluated fault localization research. The intuition for the \comb{}
combination is that several highly ranked statements, albeit covered
by failing executions, may be unrelated to the fault. Prior work
reported promising results in this combination
\cite{Wotawa:2010:FLB:1848650.1849235,Alves:2011:FUD:2190078.2190115,DBLP:conf/ecai/HoferW12,lei-mao-dai-wang-2012,slicing-sfl-repair}.
We found surprising that, despite these findings, reported nearly 5
years ago, no tool or client analyses use this combination
today. Several reasons could justify that observation. One hypothesis
to explain that observation is that results reported in prior work are
over-optimistic. For example, most prior work evaluated improvements
of \sfl{} techniques using relative metrics, which are based on the
position of the first faulty statements found in the ranking relative
to the total number of ranking statements, which is often a large
number. As such, it inflates actual improvements and deceives paper
reviewers. Ang \etal~\cite{ang-perez-van-deursen-rui-2017} recently
pointed to that fact encouraging researchers to adopt precise metrics,
such as \topatn{}
\cite{Wu:2014:CLC:2610384.2610386,Lucia:2014:FFL:2642937.2642983,Wen:2016:LLB:2970276.2970359}. This
metric reports the percentage of faults captured by a technique when
the rank is trimmed to the first N components.

The goal of this paper is to reassess whether the \comb{} combination
is worthwhile under the light of a more accurate metric and a larger
dataset. The D4J dataset is about twice as large than the biggest test
suite used in previous studies. It is worth noting that \acrAbrev{}
techniques should directly benefit from these results---either to
improve their results or to be aware they should not invest on this
integration. This study covers the following research questions:

%% ~\cite{Jin:2013:FFL:2483760.2483763,Laghari:2016:FSB:2970276.2970308,campos-etal-ase2016,DBLP:journals/stvr/LiuLNBB16,DBLP:conf/hvc/LidO16,7589823}
%% This research aims to address the doubts surrounding the efficiency of \sfl{}+\ds{} combination through the answer to the following research questions (\RQ{}):

\begin{itemize}[leftmargin=*]
%\item[] [efficiency]~\textit{How often faulty statements appear in the  most suspicious classes?}  
\item[]{\footnotesize[soundness]}~\textit{How often DS misses faulty statements?}
\item[]{\footnotesize[effectiveness]}~\textit{How much reduction in file size can DS obtain?}  
\item[]{\footnotesize[effectiveness]}~\textit{How effective is the \comb{} combination?} 
\end{itemize}

To sum, our results show that \Fix{write a paragraph about this...}

The contributions of this work are as follows:
\begin{itemize}
	\item A comprehensive study on the combination of \sfl{} and \ds{}
     for bug localization of \emph{Java} faulty programs.
%	\item Insights into the use of top-k metric to evaluate the classes with the highest suspiciousness ranks.
	\item The tools used to run the study. Benchmarks and experimental results are also publicly available.
\end{itemize}

@@

Spectrum-based fault localization (\sfl) is a statistical fault
localization technique that takes as input a test suite including at
least one failing test and reports on output a ranked list of
components likely to be in fault~\cite{FLSurvey2016,
  DBLP:conf/kbse/JonesH05, DBLP:journals/smr/LuciaLJTB14,
  DBLP:journals/jss/AbreuZGG09}. The following are given in \sfl{}: a
finite set $\mathcal{C} = \set{c_1,c_2,...,c_M}$ of $M$ system
\emph{components}\footnote{A component can be any source code artifact
  of arbitrary granularity such as a class, a method, a statement, or
  a branch~\cite{DBLP:journals/stvr/HarroldRSWY00}.}; a finite set
$\mathcal{T} = \set{t_1,t_2,...,t_N}$ of $N$ system transactions,
which correspond to records of a system execution, such as test cases;
the error vector $e = \set{e_1,e_2,...,e_N}$, where $e_i = 1$ if
transaction $t_i$ has failed and $e_i = 0$ otherwise; and an $N \times
M$ coverage matrix $\mathcal{A}$, where $\A{ij}$ denotes the coverage
of component $c_j$ in transaction $t_i$.  The pair $(\mathcal{A},e)$
is commonly referred to as
spectrum~\cite{DBLP:journals/stvr/HarroldRSWY00}. Figure~\ref{fig:spectrum-example}
shows an example spectrum.
\begin{wrapfigure}[8]{r}{0.29\textwidth}
  \vspace{-2ex}
  \hspace{-3ex}
  \centering
  \small
  \begin{tabular}{c|cccc|c}
    $\mathcal{T}$ & $c_1$    & $c_2$    & $\cdots$ & $c_M$    & $e$    \\ \hline
    $t_1$         & $\A{11}$ & $\A{12}$ & $\cdots$ & $\A{1M}$ & $e_1$  \\
    $t_2$         & $\A{21}$ & $\A{22}$ & $\cdots$ & $\A{2M}$ & $e_2$  \\
    \vdots        & \vdots   & \vdots   & $\ddots$ & \vdots   & \vdots \\
    $t_N$         & $\A{N1}$ & $\A{N2}$ & $\cdots$ & $\A{NM}$ & $e_N$  \\
  \end{tabular}
  \caption{An example spectrum.}
  \label{fig:spectrum-example}
\end{wrapfigure}
Several types of spectra exist.  The most commonly used is called
hit-spectrum, where the coverage matrix is encoded in terms of binary
\emph{hit} (1) and \emph{not hit} (0) flags, \ie{}, $\A{ij} = 1$ if
$t_i$ covers $c_j$ and $\A{ij} = 0$ otherwise.  The pair
$(\mathcal{A},e)$ serves as input to the fault localization technique.
With this input, the next step in this coverage-based technique
consists of determining what columns of the matrix $A$ resemble the
error vector $e$ the most.  For that, an intermediate component
frequency aggregator $n_{pq}(j)$ is computed $n_{pq}(j) = |\{i\mid
\A{ij}=p \wedge e_i=q\}|$. $n_{pq}(j)$ denotes the number of runs in
which the component $j$ has been active during execution ($p = 1$) or
not ($p=0$), and in which the runs failed ($q = 1$) or passed ($q =
0$).  For instance, $n_{11}(j)$ counts the number of times component
$j$ has been involved ($p = 1$) in failing executions ($q = 1$),
whereas $n_{10}(j)$ counts the number of times component $j$ has been
involved in passing executions. We then calculate similarity to the
error vector by means of applying \emph{fault predictors} to each
component to produce a score quantifying how likely it is to be
faulty.  Components are then ranked according to such likelihood
scores and reported to the user. Ochiai is one of those fault
predictors that has shown to perform well ~\cite{Pearson:2017:EIF:3097368.3097441,7390282}. \Sof{@Rui, please check if the papers are correct} The Ochiai
formula~\cite{DBLP:conf/prdc/AbreuZG06} is given by
\[\N{11}/(\sqrt{\N{11}+\N{01}} + \sqrt{\N{11}+\N{10}})\]

@@

\Mar{Sofia, I think this was way too low-level for intro and decided
  to move here. please check how to fit.}
\Fix{
A couple of different tools were designed to perform this empirical study: \morpho{} and \lithium{}. \morpho{} retrieves as an output the input for \lithium{}. \lithium{} uses the input to reduce the search domain for \sfl{} and outputs the statements that resulted from the minimization. \morpho{} uses this to update the spectrum matrix, performs the before and after \sfl{} evaluation using the corresponding matrix, and outputs the metrics that report the \sfl{} performance for both cases ~---~ before and after using \ds{}. }

@@

Following other recent studies, we used the \dfj{} benchmark in our
experiments~\cite{just-defects4j-issta2014}. The \dfj{} benchmark
includes six subjects and \numFaults{} faults.
\lang{} is a library
that provides a set of helper utilities for the {\small\texttt{java.lang}}
API. \cmath{} is a lightweight library of self-contained
mathematics and statistics components. The \closure{} is a toolset for
turning JavaScript files into smaller scripts for faster
download and execution in the browser. \chart{} is a library with a
full-featured charts user interface for Java. \jtime{} is a
lightweight library that aims to replace the default Java
{\small\texttt{java.util.Date}} classes providing simpler APIs. \mockito{} is
a mocking testing framework.\comments{ that enables the developer to simulate
the behavior of classes that cannot be used in unit testing.}
